Robinson et al. 2020 Supplemental Information: Comparing the Radiocarbon and Tree-ring Records for the Upland US Southwest

### 2020-02-05 analysis/paper/paper.Rmd
documented data

```{r setup, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  fig.align = "center",
  fig.path = "../figures/",
  message = FALSE,
  warning = FALSE,
  collapse = TRUE,
  comment = "#>",
  dev = "png",
  dpi = 300
)
library(robinson2020)
```

>>>>

```{r setup, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  fig.align = "center",
  fig.path = "../figures/",
  message = FALSE,
  warning = FALSE,
  collapse = TRUE,
  comment = "#>",
  dev = "png",
  dpi = 300
)
library(robinson2020)
library(ggplot2)
```
